Appendix A - Alternative DSDM formulations

### 2019-10-18 manuscript/appendix_a.Rmd
--amend

Input:
- `X`: a $N$x$K$ design matrix for vital rate regression sub-models
- `beta_F`: a $K$x$L$ matrix of regression coefficients for log-fecundity for each species
- `beta_S`: a $K$x$L$ matrix of regression coefficients for logit-survival for each species
- `alpha_F`: a $K$x$K$ matrix of the intra- and inter-specific effects of population density on log-fecundity
- `alpha_S`: a $K$x$K$ matrix of the intra- and inter-specific effects of population density on logit-survival
- `gamma`: a (positive) vector of length $K$ for the differences in logit-survival betwen adults and juveniles for each species

```{r biotic_interactions}
# matrix of weights for each lifestage to the population density of each species
# (for density-dependence effects)

A_t_function <- function(state, iter, log_F, logit_S, alpha_F, alpha_S, gamma, dd_weights) {

  # apply density-dependent effects
  N <- state %*% dd_weights
  log_F_t <-  base_log_F + N %*% alpha_F
  logit_S_A_t <- base_logit_S + N %*% alpha_S

  # get vital rates for each site/species
  F_t <- exp(log_F_t)
  S_A_t <- ilogit(logit_S_A_t)
  S_J_t <- ilogit(sweep(logit_S_A, 2, gamma, "-"))

  # combine into a single matrix such that that each species has adjacent lifestages
  top <- rbind(F_t * S_J_t, F_t * S_A_t)
  bottom <- rbind(S_J_t, S_A_t)
  dim(top) <- c(nrow(N), ncol(N) * 2)
  dim(bottom) <- c(nrow(N), ncol(N) * 2)
  A_t <- abind(top, bottom, along = 3)
  A_t

>>>>

- `X`: a $N$x$K$ design matrix for vital rate regression sub-models
- `beta_F`: a $K$x$L$ matrix of regression coefficients for log-fecundity for each species
- `beta_S`: a $K$x$L$ matrix of regression coefficients for logit-survival for each species
- `alpha_F`: a $K$x$K$ matrix of the intra- and inter-specific effects of population density on log-fecundity
- `alpha_S`: a $K$x$K$ matrix of the intra- and inter-specific effects of population density on logit-survival
- `gamma`: a (positive) vector of length $K$ for the differences in logit-survival betwen adults and juveniles for each species

```{r biotic_interactions}
A_t_function <- function(state, iter, log_F, logit_S, alpha_F, alpha_S, gamma, dd_weights) {

  N <- state %*% dd_weights
  log_F_t <-  base_log_F + N %*% alpha_F
  logit_S_A_t <- base_logit_S + N %*% alpha_S

  F_t <- exp(log_F_t)
  S_A_t <- ilogit(logit_S_A_t)
  S_J_t <- ilogit(sweep(logit_S_A, 2, gamma, "-"))

  top <- rbind(F_t * S_J_t, F_t * S_A_t)
  bottom <- rbind(S_J_t, S_A_t)
  dim(top) <- c(nrow(N), ncol(N) * 2)
  dim(bottom) <- c(nrow(N), ncol(N) * 2)
  A_t <- abind(top, bottom, along = 3)
  A_t
